Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-14 README.Rmd
update draft

#merge data 
zip = zip_dtc %>% left_join(zip_n) %>%
  left_join(zip_covid)

@@

#list of zip to zoom in
zip_kcmo = unique(as.character(zip_covid$ZIP))

#zip code choropleth for covid infection rate
zip_choropleth(zip_covid %>% mutate(region = as.character(ZIP), value = rate*100), 
               #state_zoom = ec_states, 
               zip_zoom = zip_kcmo,
               title      = "",
               legend     = "COVID-19 Infection Rate") + coord_map()

@@

Influx of covid-related requests due to COVID-19

```{r}
# covid related request by zip code 
zip_covid_311 = dat %>% group_by(ZIP) %>% 
  summarise(
    n = n(),
    n_allcovid = sum(allcovid))

#scatter plot
zip_covid %>% left_join(zip_covid_311) %>%
  ggplot(aes(x = rate*100, y = n_allcovid, size = n, col = n))+ 
  geom_point()+
  geom_smooth(method=lm)+
  labs(x= "COVID-19 infection rate", y="Volume of covid-related requests")+
  theme_bw()+
  theme(legend.position = "none")

#reg
summary(lm(rate*100 ~ n_allcovid, 
           data = zip_covid %>% left_join(zip_covid_311)))

@@

```{r zip_vol, fig.height = 8,fig.width=8}
#scatterplot
zip %>%
  ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~CATEGORY, scale = "free_y")+
  theme_bw()+
  theme(legend.position = "none")
```

@@

```{r zip_dtc, fig.height = 3,fig.width=8}
#scatter plot
zip %>% 
  left_join(diff) %>%
  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  ggplot(aes(y = daytoclose_diff, x = rate*100, size = daytoclose_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y")+
  labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
  theme_bw()+
  theme(legend.position = "none")
```

```{r zip_dtc2, fig.height = 3,fig.width=8}
# #scatterplot
# zip %>% 
#   filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
#   ggplot(aes(y = daytoclose_diff, x = n_diff, size = n_2019, col = ZIP))+
#   geom_point()+
#   geom_smooth(method=lm)+
#   facet_wrap(~CATEGORY, scale = "free")+
#   theme_bw()+
#   theme(legend.position = "none")
```

@@

#combine reg 
screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
          omit.coef = "after|rate|Intercept", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
          custom.coef.names = "DiD effect"#,
        #file = "reg.doc"
          )

>>>>

# volume of covid-related of requests
zip_covid_311 = dat %>%
  group_by(ZIP) %>% 
  summarize(n = n(), n_allcovid = sum(allcovid)) %>% na.omit()

#merge data 
zip = zip_dtc %>% left_join(zip_n) %>%
  left_join(zip_covid) %>%
  left_join(zip_covid_311)

@@

#list of zip to zoom in
zip_kcmo = unique(as.character(zip_covid_311$ZIP))

#zip code choropleth for 
zip_choropleth(zip_covid_311 %>% mutate(region = as.character(ZIP), value = n_allcovid), 
               zip_zoom = zip_kcmo,
               title      = "",
               legend     = "Volume of Covid-related Requests") + coord_map()

@@

```{r}
#scatterplot
dat %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR, ZIP) %>%
  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
  dcast(ZIP ~ CREATEYR) %>% 
  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`) %>%
  left_join(zip_covid_311) %>% 
  ggplot(aes(y = daytoclose_diff, x = n_allcovid, size = n, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  theme_bw()+
  theme(legend.position = "none")

#linear regression
summary(lm(daytoclose_diff~n_allcovid, data = dat %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR, ZIP) %>%
  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
  dcast(ZIP ~ CREATEYR) %>% 
  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`) %>%
  left_join(zip_covid_311)
))

@@

pretrends

```{r}
rank10 = zip_covid_311 %>% 
  mutate(group = cut(zip_covid_311$n_allcovid,breaks = quantile(zip_covid_311$n_allcovid,seq(0,1,0.2)),labels = FALSE,include.lowest = TRUE))

dat %>% left_join(rank10 ) %>% filter(group %in%c(1,5)) %>% 
  group_by(group,date) %>% 
  summarise(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>% 
  ggplot(aes(x = date, y = daytoclose, group = group, col = as.factor(group)))+
  geom_line(lwd= 1.5)+
  theme_bw()

@@

```{r zip_dtc, fig.height = 6,fig.width=8}
#scatterplot
zip %>%
  filter(CATEGORY != "Data Not Available") %>%
  ggplot(aes(y = daytoclose_diff, x = n_allcovid, size = n_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~CATEGORY, scale = "free", ncol=5)+
  theme_bw()+
  theme(legend.position = "none")
```

@@
